---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# SDS 235: Visual Analytics - Final Project

## A Shiny App exploring NYC Civilian Complaints about the NYPD

Our app is deployed on shinyapps.io at this [link](https://marium.shinyapps.io/sds235-final-project/). You could also run it by cloning this repository locally and running the `app.R` script!

### Components of this repository

Our project includes the following files/folders:

- `app.R` contains the `server` and `ui` of our app
- the other `.R` files contain components of our app that are sourced into `app.R`
- `footer.hmtl` contains HTML and CSS code for our footer
- the `scratchpads` folder contains our data wrangling and visualizations before they go into the shiny app
- the `data` folder contains the main data for our project. It is called **Civilian Complaints Against New York City Police Officers**. It was retrieved on April 29, 2021 from [ProPublica](www.propublica.org/datastore/dataset/civilian-complaints-against-new-york-city-police-officers).

### Required Packages 

Our app requires the following R packages which are all available for download from CRAN: 

- tidyverse
- shiny
- shinythemes
- leaflet
- plotly
- here
- RColorBrewer
- kableExtra
- htmltools
- reactable

You can run the following code in your console to install all these packages:

```{r, eval=FALSE}
install.packages(c(
  "tidyverse", "shiny", "shinythemes",
  "leaflet", "plotly", "here",
  "RColorBrewer", "kableExtra",
  "htmltools", "reactable"
))
```

GitHub repo: https://github.com/mariumtapal/sds235-final-project

Group Members:

- Marium Tapal
- Eleni Partakki
- Elisabeth Nesmith